Academic Advancement Advice: Author Articles as A.~A.

### 2018-03-12 trunk/citations/paper.tex
More in paper, tourney, figures

\documentclass[twocolumn]{article}
\usepackage[top=1.1in, left=0.85in, right=0.85in]{geometry}

@@

This is not my first segmentation fault---let me tell you!---so I knew
what to do. I debugged the program, adding assertions using a
\verb+CHECK+ macro that aborts if its condition is violated. I
eventually determined that the bug must be inside the JSON library
itself, since the segmentation fault happened between two
\verb+CHECK+s where the only code being run was JSON library code. So,
deciding that perhaps its $100\%$ correctness benchmark score was
overstated, I downloaded and repeated the process with the other,
faster (i.e., more slapdash) parser. Of course this parser has a
different API so I needed to rewrite my program. (The program is very
simple so this was the fastest step; however, getting the library
properly incorporated and compiling and then learning its API was
still a computer science chore.) Once my program was rid of the old
crashy library, I ran it, and it produced this result
\begin{verbatim}
  [Segmentation fault
\end{verbatim}
Since these two libraries produced the same result, either
segmentation violation must be part of the JSON specification, or the
bug is instead elsewhere in the program. After reducing the program to
a fairly simple test case, I determined that it must be some kind of
``Heisenbug'' whereby an earlier piece of code was corrupting the heap
or similar, causing a later crash only when present. This was not my
first Heisenbug---let me tell you!---so I knew what to do. However,
not being able to use Valgrind on Windows (did I mention that I'm
using Cygwin and mingw64 on the eponymous Windows~7 by the way? Why am
I doing that?), I booted Linux in a virtual machine, installed the 87
security updates that had been released since I last booted this
virtual machine a few months ago, and compiled my program there. I
then needed to move one of the JSON files to the virtual computer to
test, without having to download 130 GB from the internet again, but
the file was apparently too large to transfer using the mysterious
``Drag and drop to virtual machine'' functionality. I recalled that
VirtualBox can mount a shared folder from the host machine if you edit
the \verb+/etc/fstab+ file to contain the correct arcane magic, and
that I had performed this ritual before, but then had commented-out
that line in ``rescue mode'' because I also learned that having this
line present during the boot process causes a kernel panic. So I
temporarily reinstated the line and mounted the drive and copied the
gigantic file into the virtual machine and then removed the dangerous
magic from the f-stab for f-safety.

@@

Since Linux was no help debugging, I returned to Windows~7 and tried
single-step debugging. Here I discovered that the crash in my minimal
test case was occurring when using \verb+cerr+. Specifically, the
second thing sent to \verb+cerr+ would produce a segmentation fault.
I then recalled that the \verb+CHECK+ macro uses \verb+cerr+ and
also found code I had written in the Year 2014

The original ``bug'' was a violated assumption: I assumed,
optimistically, that if the article had an {\tt author} field then
the author would be a string. I accounted for a missing author,
an author that was the empty string, but not {\tt author: null}.

multiple hypothesized causes:

 - When doing a

300 GB of json woes

@@

Adopting an all-'A' affect also advances articles.
Awesome!

@@

capinha para celular horizonte artificial iphone

>>>>

\documentclass[twocolumn]{article}
\usepackage[top=1.1in, left=0.85in, right=0.85in]{geometry}
% \usepackage[utf8]{inputenc}

@@

This is not my first segmentation fault---let me tell you!---so I knew
what to do. I debugged the program, adding assertions using a
\verb+CHECK+ macro that aborts if its condition is violated. I
eventually determined that the bug must be inside the JSON library
itself, since the segmentation fault happened between two
\verb+CHECK+s where the only code being run was JSON library code. So,
deciding that perhaps its $100\%$ correctness benchmark score was
overstated, I downloaded and repeated the process with the other,
faster (i.e., more slapdash) parser. Of course this parser has a
different API so I needed to rewrite my program. (The program is very
simple so this was the fastest step; however, getting the library
properly incorporated and compiling and then learning its API was
still a computer science chore.) Once my program was rid of the old
crashy library, I ran it, and it produced this result
\begin{verbatim}
  [Segmentation fault
\end{verbatim}
Since these two libraries produced the same result, either
segmentation violation must be part of the JSON specification, or the
bug is instead elsewhere in the program. After reducing the program to
a fairly simple test case, I determined that it must be some kind of
``Heisenbug'' whereby an earlier piece of code was corrupting the heap
or similar, causing a later crash only when present. This was not my
first Heisenbug---let me tell you!---so I knew what to do. However,
not being able to use Valgrind on Windows (did I mention that I'm
using Cygwin and mingw64 on the eponymous Windows~7 by the way? Why am
I doing that?), I booted Linux in a virtual machine, installed the 87
security updates that had been released since I last booted this
virtual machine a few months ago, and compiled my program there. I
then needed to move one of the JSON files to the virtual computer to
test, without having to download 130 GB from the internet again, but
the file was apparently too large to transfer using the mysterious
``Drag and drop to virtual machine'' functionality. I recalled that
VirtualBox can mount a shared folder from the host machine if you edit
the \verb+/etc/fstab+ file to contain the correct code words, and
that I had performed this ritual before, but then had commented-out
that line in ``rescue mode'' because I also learned that having this
line present during the boot process causes a kernel panic. So I
temporarily reinstated the line and mounted the drive and copied the
gigantic file into the virtual machine and then removed the dangerous
magic from the f-stab for f-safety.

@@

Since Linux was no help debugging, I returned to Windows~7 and tried
single-step debugging. Here I discovered that the crash in my minimal
test case was occurring when using \verb+cerr+. Specifically, the
second thing sent to \verb+cerr+ would produce a segmentation fault. I
then recalled that the \verb+CHECK+ macro uses \verb+cerr+ and now saw that
the \verb+[+ in \verb+[Segmentation fault+ was probative, for this
was the location of the original crash:
\begin{Verbatim}[fontsize=\small]
    std::cerr << "[" << pretty_date_.HumanDate() << "] "
              << file << ":" << line << ": ";
\end{Verbatim}

Of course, inside \verb+HumanDate()+ I found a hasty patch I had
installed in A.D.~2014 called ``make logging not spit garbage on
mingw,'' suggesting that I had encountered and misdiagnosed this issue
in the past. Although this led me on a minor herring (e.g. is
\verb+__MINGW32__+ defined when cross-compiling for x86\_64?)
HumanDate just returned \verb+"mingw"+, so this really was a problem
with \verb+std::cerr+ crashing on the second thing printed with it
(i.e., with the returned \verb+ostream+).

Minimizing the test case, this bug only occurred after reading a large
file all in one syscall (for ``performance'', even though doing these
huge reads basically locks up my machine). Specifically the file was
2,105,319,548 bytes, which is $98\%$ of $2^{31}$, suggesting the
possibility of integer overflow in some buffer-sizing code in the
weird Cygwin or mingw wrappers for \verb+fread+, \verb+fstat+, etc.
This could plausibly cause corruption of the \verb+cerr+ ostream,
which is probably part of the same code.

Preparing to at least make a bug report if not try to fix it, I
upgraded my compiler and runtime from GCC version 5.1.0 to 6.4.0,
and the problem completely went away. Since Valgrind also agreed
that there was no issue, I chalked this one up to simply an internal
C runtime bug that someone else found and fixed in the last 2 years.
Thanks!

With \verb+cerr+ fixed, I could now easily see the original ``bug'',
which was a violated assumption: I expected (and \verb+CHECK+ed),
optimistically, that if the article had an {\tt author} field then the
author would be a string. I accounted for a missing author, an author
that was the empty string, but not {\tt author: null}. Thanks!

Finally, I could run the author and citation tallier on all of the
JSON files. However, two of the files appeared to be empty. Although
this was only a small percentage of the articles, I did not want to
skip any because it's possible that they are arranged in a non-random
order (e.g. alphabetically!) and that this would bias the results. I
learned that although the AMiner database is helpfully split into
files each containing one million articles, for ease of handling, two
of these files are nonetheless slightly larger than $2^{31}$ bytes. Such
files cannot be cleanly sized with \verb+fstat+ (the \verb+st_size+
field has type \verb+off_t+, a signed 32-bit type in POSIX) and even
if you follow the standard advice of just treating it as unsigned
anyway, \verb+fread+ will simply fail when asked to read such a large
chunk\footnote{
%
  Curious why I am even using {\tt fstat} and {\tt fread}? I have my
  own library routine for reading a file into a string. When working
  with large files it's useful to avoid copying, because the contents
  of the file may be a significant fraction of all RAM---copying is
  not only expensive, but might temporarily exceed the available RAM.
  So, you need to allocate the buffer ahead of time and avoid resizing
  it (which often also performs a copy). It seems like something that
  everyone would want to do, but it's ridiculously hard to do portably
  in C or C++. Specifically, there seems to be no way to actually know
  the size of a file so that you can size the buffer ahead of time.
  For example, {\tt fseek} to {\tt SEEK\_END} and {\tt ftell} does
  {\em not} work (it has {\em undefined behavior}). The {\tt st\_size}
  field from {\tt stat} also does not give correct results e.g. when
  reading from the {\tt /proc} filesystem. My routine attempts to
  guess the size of the file and perform a single read in the case
  that the guess is correct, while still usually avoiding copying or
  needless work in the case that it's an under- or over-estimate.
%
} despite the fact that it takes \verb+size_t+, an unsigned type. (?!)
So, another afternoon spent doing Computer Science. But all you need
to do of course is perform multiple sequential reads.

Finally, the trivial task of counting the number of articles and
citations per author could be completed.

This citation database is very noisy. About $1.6\%$ of articles have
no authors, and another $1\%$ have a blank (or {\tt null}) author. I
verified the comprehensiveness of the dataset by finding my own author
record(s)\footnote{This paper is published under the pseudonym A.~A.,
  standing for Awesome Author, obviously in order top increase its
  citation rate. Normally I publish as Tom Murphy VII, which can be
  found in citations with many broken variations, such as ``Vii, T.''}
and 275 citations ({\bf Yeah!!}). I also spot-checked that the database
includes prestigious conferences, which it does, at least including
the ``article'' {\em A Record of the Proceedings of SIGBOVIK 2008},
with author {\em Pennsylvania USA}. It was necessary to normalize
author names to remove punctuation, weird unicode stuff like non-breaking
spaces, javascript-encoded newlines and nul-bytes, and so on. There
are many strange authors in the database, such as
\begin{itemize}
\item capinha para celular horizonte artificial iphone \quad(no citations)
\item +0aaaaaabablaaaaaea\&\#xa \quad(no citations)
\item a h poop \quad(4 citations)
\item john mcm anus\footnote{Presumably a hostile citation of John McManus.} \quad(2 citations)
\item coffee hour \quad(0 citations)
\item nominate com registering dad domains since \quad(0 citations)
\item a a \quad(195 citations)
\item a a a a m islam \quad(6 citations)
\end{itemize}

On the other hand, from this hand-picked sample we can already see the
citation advantage of having a name that's alphabetically early. Some
authors seem to have already intuited this fact.

\section{Analysis}

Author names appear in both ``Firstname Lastname'' order and
``Lastname Firstname'' (when this grammar is even applicable).
Therefore, I analyzed alphabetizing from front to back (by
space-separated token) as well as back to front. I also rejected a
large number entries when I could not place the name in alphabetical
order because its first character was not ASCII. Later non-ASCII
characters are OK, and are just sorted by their UTF-8 encodings (or
whatever garbage is in the file). This of course produces a bias
(excluding authors who write their names in e.g. Cyrillic and CJK
scripts), although it's not clear how to assess the alphabetical
hypothesis for them.

To visualize the data, I produced a cumulative distribution function
(CDF) for both articles and citations. Considering each author in
alphabetical order, I keep a running total of how many articles and
how many citations have been seen so far. The x-coordinate is the rank
of the author (its index in the sorted list) and the y-coordinates are
the fraction of articles (or citations) seen so far. The CDFs for the
forward and backward token orders are in Figure~\ref{fig:authorcdf}.

\begin{figure}
  \begin{center}
  \includegraphics[width=0.44 \textwidth]{authorstats-forward}
  \includegraphics[width=0.44 \textwidth]{authorstats-backward}
  \end{center}
  \caption{ Author CDFs for (a) forward token order and (b) backward
    token order. (For example, (a) treats {\tt tom murphy vii} as
    coming between {\tt tom marphy} and {\tt tom myrphie vxx} and (b)
    treats it as coming between {\tt zzz murphx vii} and {\tt a
      viii}.) The x-axis is the author's position alphabetically among
    all authors. The blue lines are the fraction of all citations seen
    so far, and the red lines the same for articles. The lines must
    meet at $(0,0)$ and $(1,1)$ by definition. When the blue line is
    above the red, the number of citations is outpacing the number of
    articles for authors alphabetically before this point. Both show a
    bias towards the early alphabet, with the forward direction being
    more dramatic (for basically the entire range). The backward range
    briefly shows the opposite bias (crossing over at author
    \#5,400,000, ``ojars biskaps''), suggesting that the best names
    may be alphabetically early but in the {\em B}s, not {\em A}s. The
    poorer performance of A-names may be due to authors attempting to
    ``game the system'' by publishing with names like ``a a.''
  } \label{fig:authorcdf}
\end{figure}

These CDFs show that---as expected!---there is a bias towards citing
authors alphabetically early, whether we order alphabetically by
``first name'' or ``last name.''

There are multiple hypothesized causes:

- When writing a last-minute ``related work'' section, authors seek
  out work

- Some academics try to \verb+fread+ all papers into memory, but
  it fails on the file that's just slightly larger than $2^{31}$ bytes,
  and so the papers therein don't get cited, and those papers are
  alphabetically in the middle or end of the alphabet.

% 
% 313779.  書評	29582	1	0.000068
% 313778.  インタビュー	20547	1	0.000097
% 313777.  facharzt	85315	9	0.000117
% 313776.  f3d	125257	15	0.000128
% 313775.  recenzja	63568	8	0.000142
% 313774.  newhaven	13296	1	0.000150
% 313773.  secrétaire	12267	1	0.000163
% 313772.  zahnarzt	17958	2	0.000167
% 313771.  libguides	389727	72	0.000187
% 313770.  硏究	12961	2	0.000231
% 313769.  그	15984	3	0.000250
% 313768.  kitas	7713	1	0.000259
% 313767.  シンポジウム	18539	4	0.000270
% 313766.  特集	878011	240	0.000274
%

\begin{figure}
  \begin{center}
  \includegraphics[width=0.475 \textwidth]{wordstats}
  \end{center}
  \caption{ CDF for words arranged alphabetically. This is just as
    in Figure~\ref{fig:authorcdf}, but since each entry is a single
    word, there is no need to treat forward and backward differently.
    Again, we see a small alphabetical bias, with citations leading
    articles for most of the range. In fact, papers that include the
    very first word, ``a'', are cited $1.3\times$ as often as the
    average paper. Other common and advantageous words are visible
    as clear bumps. (See Section XXX)
  } \label{fig:wordcdf}
\end{figure}

% Tourney -- what is wrong here?
%  1000.000 Mrounds:
%  (69.66 vs. 72.69 Gcit) (6.72 vs. 7.20 Gart) (0.281 vs. 0.295 Gwin)
%  (0.958361 L:R cit) (0.933736 L:R art) (0.280867 vs. 0.295327 win rate)

@@

Adopting an all-'A' affect also advances articles. Although affairs
are abbreviated, adequate abstracts abound: Astronomy, asthma,
atmospheric acclimatization, autobiography, Azerbaijani accents,
acceleration, and abundant alternatives.

% arranged alphabetically.

Awesome!

@@

u fucks
a a fucks
